\chapter{Evaluation and Presentation}
    \section{Evaluation Phase}
        Evaluation is the phase in which we're trying to match evidence elements with the required elements that are part of a legal theory.\\
        What are the elements of the legal theory for kid's bad things are:
        \begin{itemize}
            \item User has pictures, found trough carving or search. We need to demonstrate that they are what we are saying them are.
            \item Willingly detaining? We can propose facts to support or not this legal theory: were the images in a specific folder, sorted, access dates, in the cache of the browser?
            \item If the images were deleted, we have not the metadata to understand if they were willingly detained.
        \end{itemize}
    \section{Items to evaluate}
        The elements to support the indictment.
        Alternative explanations to the elements: does the elements univocally support the theory or there is another theory? Defense experts job. Prosecutor expert witness, may or may not be obliged to search for them.
        We can also analyze something which comes from another person's investigation, so when analizing evidence or sources of evidence, we know that (?) 
        Analyzing what can be said, what cannot, and what further experiments would be needed to say more: sometimes defense can under certain circumstances ask the prosecutor to do something, the data is not there at the moment, how likely is this data to go in my direction or in the other?\\
        If you're working as Prosecutor's expert witness, the answer is to perform the experiment to retrieve what's missing. For the expert witness of the defense, this is an important consideration.