MOST DRIVES HERE ARE SSD
    most cellphones drive work in a similar way to ssd 
    they're made of nand flash, permanent, fast, cheap 
    on the surface they work exactly the same way as HDD
    You don't see any difference 
    But the two technologies are different.

    Nand flash has a limited lifetime 
    so, since we write and erase a lot, we need to figure out ways to make these last long enough
    
    Another difference is that nand memories have blocks from 16 to 512 kb long
    blocks in ssds can only be written completely
    when the block is rewritten it is all rewritten
    and before, it has to be blanked
    the combination of this things, + fast time for reading
    but you want the hdds and ssd to work in the same way 
    ssd had to possibly be put inside an os that didn't knew about the ssd 
    FTL controller fakes the fact of the drive working like an HDD.
    It lies to the operating system 

    It lies about geometry 

    We write a lot, rewrite, (some files are never rewritten)
    If we took these files and place them on the drive at random, the cells for the os files stay uguali
    The files instead get spaccati subito   
    FTL swaps them doing wear leveling 

    another thing we can do is to maybe keep things in a cache. SSD drives have large onboard cache to write on the drive only when it is really necessary  
    (Write caching)
    Also compressing data uses less blocks.
    Redundant space in ssds 

    + if we want to write to a cell we first need to blank it, which is not the same for hard drives.
    Blankning takes time. So, to make ssd drives more performant, when we have time we start blanking.
    In order to start blanking we need to have from the os a list of the data areas that can be blanked
    This process is called trimming.
    This thing makes more difficult to recover undeleted data. Now we can no more exploit the laziness of the OS.
    When SSDs were not supported yet by OS, controller developers tried to do garbage collection. To figure out alone the FTL what to blank,
    Now they're supported, so trimming.

    Bad block handling.

    All of these summarized makes the FTL lie on the position of the blocks, on the internal structure of the drive, 
    same situation of memory allocation in processes/threads
    the same for usb sticks. FTL on USB sticks is cheap and do not perform all of the operations.
    hash of usb sticks change every time because of the shitty FTL 
    Since the drive performs trimming, and it happens everytime we're not reading or writing. When we connect a write locker, the drive starts trimming.